humanCdGF_predict_cfu

### 2016-11-21 code/HumanCdGF_predict_cfu.Rmd
add cfu om_loo validation

>>>>

# one mouse leave one out
om_loo_pred <- c()
for(i in 1:iters){
    set.seed(i)
    one_mouse <- one_mouse_df %>% 
      group_by(cage_id) %>% 
      sample_n(1) %>% ungroup() 
    for (n in unique(as.character(one_mouse$cage_id))){
      train <- filter(one_mouse, !cage_id == n)
      test <- one_mouse_df %>% 
        filter(cage_id == n)
      set.seed(seed)
      rf_om_loo <- randomForest(log_cfu_med ~ ., data = select(train, -mouse_id, -cage_id),
                                ntree = 500)
      om_loo_pred <- rbind(om_loo_pred,
                           data.frame(select(test, mouse_id, cage_id, log_cfu_med),
                           predicted=predict(rf_om_loo, test)))
    }
      #import_df <- importance(rf_om)
      #colnames(import_df)[1] <- paste(train$mouse_id, collapse = ' ')
      #om_import_otus <- merge(om_import_otus, import_df, by.x = 'otu', by.y = 'row.names')
      #om_import_otus <- select(om_import_otus, -IncNodePurity)
}
om_loo_rsq <- 1 - (sum((om_loo_pred$log_cfu_med - om_loo_pred$predicted)^2)/
               sum((om_loo_pred$log_cfu_med - mean(om_loo_pred$log_cfu_med))^2))

om_loo_pred <- rename(om_loo_pred, observed = log_cfu_med)

cor.test(om_loo_pred$observed, om_loo_pred$predicted, method = 'pearson')
